---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file - rmarkdown::render('README.Rmd', output_format = 'github_document', output_file = 'README.md') -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages, include=FALSE}
library(tidyverse)
```

## Molodcov GT

This repository contains a Ground Truth dataset for Komi Molodcov orthography, and attempts to evaluate the coverage and quality of the materials within it. The goal is to have there clear metrics for different OCR models. It is intended be used in combination with other Ground Truth package that contain texts in this orthography.

```{r metadata, echo=FALSE}

url1 <- "http://fennougrica.kansalliskirjasto.fi/handle/10024/87597"
book1 <- "Кыдзи да мый силосуйтны колхозъяслы"
  
metadata <- tribble(
  ~page,                      ~set,    ~handle, ~source, ~author, ~translator,
  "kpv_3-1691_1931_0005.tif", "train_1", url1, book1, "Гиннов, В." , "Шеболкин Павел Андреевич", 
  "kpv_3-1691_1931_0006.tif", "train_1", url1, book1, "Гиннов, В." , "Шеболкин Павел Андреевич",
  "kpv_3-1691_1931_0007.tif", "train_2", url1, book1, "Гиннов, В." , "Шеболкин Павел Андреевич",
  "kpv_3-1691_1931_0008.tif", "train_2", url1, book1, "Гиннов, В." , "Шеболкин Павел Андреевич",
  "kpv_3-1691_1931_0009.tif", "train_3", url1, book1, "Гиннов, В." , "Шеболкин Павел Андреевич",
  "kpv_3-1691_1931_0010.tif", "train_3", url1, book1, "Гиннов, В." , "Шеболкин Павел Андреевич")

metadata %>% knitr::kable()
```

```{r read_lines, echo=FALSE}
gt <- dir("data", pattern = "*.gt.txt", recursive = TRUE, full.names = TRUE) %>%
  map_df(~ {tibble(file = .x,
                   text = read_lines(.x))})

```

The Ground Truth contains at the moment `r nrow(gt)` lines.

## Rare letters

Following letters occur only 3 times or less.

```{r plot_characters, echo=FALSE}
gt %>%
  mutate(character = str_split(text, "")) %>%
  unnest(character) %>%
  count(character) %>%
  arrange(n) %>%
  filter(n <= 3) %>% knitr::kable()

```


